Results

### 2018-03-16 02_analysis.Rmd
Rearrange and add skeleton for likelihood
Add link to Stan discussions over posterior_linepred

## Visualize important variables

@@

The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution. But this approach here mirrors using `predict()` to combine all the coefficients and intercept terms in a regular frequentist linear model and it's probably appropriate for this situation because all the coefficients are actually linked together behind the scenes and create group mean estimates. If I use the full force of `posterior_predict()`, I add more uncertainty with each added coefficient (so in a 2×2×2 version, the 8th condition is actually the sum of all 8 coefficients, which means it gets 8 levels of uncertainity, which is probably excessive). But we do it both ways too, just to be on the safe side.

@@

>>>>

# Visualize important variables

## Prior favorability towards NGOs

@@

The Stan people really really don't like `posterior_linepred()`, since it throws away a lot of the uncertainty that comes from actually getting a posterior distribution (like, [they didn't even want to invent it, and then when they did they wanted to hide it](https://github.com/stan-dev/rstanarm/issues/85), and it has a big warning in the documentation). But this approach here mirrors using `predict()` to combine all the coefficients and intercept terms in a regular frequentist linear model and it's probably appropriate for this situation because all the coefficients are actually linked together behind the scenes and create group mean estimates. If I use the full force of `posterior_predict()`, I add more uncertainty with each added coefficient (so in a 2×2×2 version, the 8th condition is actually the sum of all 8 coefficients, which means it gets 8 levels of uncertainity, which is probably excessive). But we do it both ways too, just to be on the safe side.

@@

# Likelihood of donation
